---
title: "Quality report for CosMx"
date: "`r Sys.Date()`"
author: "JiangLab"
output: 
  rmdformats::downcute:
params: 
  parameter1: "/bmbl_data/yuzhou/collaborative/Sizun_lab/Protocol_CosMX/CosMXQC/Data/BPC23NE_HTMA541_section9_3ugml_1"
  parameter2: "/bmbl_data/yuzhou/collaborative/Sizun_lab/Protocol_CosMX/CosMXQC/Data/BPC23NE_HTMA541_section9_3ugml_2"
editor_options: 
  chunk_output_type: console
---

```{css, echo = FALSE}
h1, h2, h3 {
  text-align: center;
}
p {
  font-size: 16px;
}
#toc > ul {
  margin-left: 5px;
  padding-left: 0;
}
#toc > ul li ul li {
  list-style: disc;
  max-height: none; 
  overflow: visible; 
  transition: none; 
  color: grey; 
}
#toc > ul li.active ul li  {
  max-height: none;
  transition: none;
  color: grey; 
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message = FALSE, warning = FALSE)
knitr::opts_chunk$set(fig.width = 8, fig.height = 4, dpi = 120)
```

```{r FindFillName}
library(ggplot2)
library(dplyr)
library(tidyr)
library(ggpubr)
library(stringr)
library(purrr)
library(sf)
library(patchwork)
source(here::here("functions.R"))

# A_input_file = params$parameter1
# B_input_file = params$parameter2


path_flat_files <- c(
  "/mnt/nfs/storage/CosMX/Indepth_TMA971_section01_v132/AtoMx/flatFiles/Indepth_EBV971_CosMx/", 
  "/mnt/nfs/storage/CosMX/Indepth_TMA971_section02_v132/AtoMx/flatFiles/Indepth_EBV_971_Fusion_CosMx/"
)
path_logs_files <- c(
  "/mnt/nfs/storage/CosMX/Indepth_TMA971_section01_v132/AtoMx/RawFiles/Indepth_EBV97.1_CosMx/Logs/", 
  "/mnt/nfs/storage/CosMX/Indepth_TMA971_section02_v132/AtoMx/RawFiles/240209_INDEPTH_FusionCosMx_10/Logs/"
)

list_path_all_files <- map2(
  path_flat_files, 
  path_logs_files, 
  ~ find_all_files(path_flat_files = .x, path_logs_files = .y)
)

list_combined_data <- map(list_path_all_files, ~ load_all_files(.x), .progress = TRUE)


# Parameters
all_fov <- map(list_combined_data, ~ {unique(c(.x$metadata_sub$fov, .x$tx_sub$fov))})
nchar_fov <- all_fov %>% unlist() %>% as.character() %>% nchar() %>% max()
list_run_name <- list_combined_data %>% map(~ unique(.x$metadata_sub$Run_Tissue_name))
list_all_cell <- list_combined_data %>% map(~ .x$metadata_sub %>% distinct(fov, cell))

target <- colnames(list_combined_data[[1]]$exprMat_sub)
target <- target[!target %in% c("fov", "cell_ID", "cell")]
target_false <- target[grepl("SystemControl", target)]
target_negative <- target[grepl("Negative", target)]
target_real <- setdiff(target, c(target_false, target_negative))
df_target_type <- bind_rows(
  data.frame(target = target_real, target_type = "Gene"), 
  data.frame(target = target_false, target_type = "SystemControl"), 
  data.frame(target = target_negative, target_type = "Negative")
) %>% 
  mutate(across(target_type, ~ factor(.x, levels = c("Negative", "SystemControl", "Gene"))))
```

# CosMX introduction

CosMx SMI is currently the only spatial platform enabling the quantification of 1000+ targets at subcellular resolution for maximum biological insight. The CosMx SMI in-situ chemistry is designed to enable high-plex and high-resolution with probes and fluorophores designed to reduce optical crowding limitations, allowing multiplexing probes to 1000 unique transcript species and beyond. In addition to high-plex, CosMx SMI also achieves high resolution. Target localization accuracy of ∼50 nm in the XY plane allows for targeting of \<1kb transcripts with no loss in performance.


# Overview (per FOV)

## Global-View of Entire Run {.tabset .tabset-pills}
```{r, results='asis'}
list_output <- list_combined_data %>% 
  map(~ .x %>% global_summarize_Fov() %>% GlobalViewTable_func())

for (i in seq_along(list_output)) {
  cat("\n\n### ", list_run_name[[i]], "\n")
  print(list_output[[i]])
}
```


## Profiling Position (FOV Index) {.tabset .tabset-pills}
```{r, results='asis'}
list_output <- list_combined_data %>% 
  map(~ .x %>% plt_fov_position())
cat("\n\n### ", "Combined\n")
print(plt_combined(list_output))
for (i in seq_along(list_output)) {
  cat("\n\n### ", list_run_name[[i]], "\n")
  print(list_output[[i]])
}
```


## Unique Transcripts  {.tabset .tabset-pills}
```{r, results='asis'}
list_output <- list_combined_data %>% 
  map(~ .x %>% plt_n_unique_Fov())
fill_range <- get_pdata_range(list_output, "n", 1, vmin = 1, vmax = NULL) %>% log10()
list_output <- list_output %>% 
  map(
    ~ .x + 
      scale_fill_continuous(type = "viridis", limits = fill_range) +
      scale_x_discrete(labels = ~ .x %>% str_pad(width = nchar_fov, pad = "0"))
  )

cat("\n\n### ", "Combined\n")
print(plt_combined(list_output))
for(i in seq_along(list_output)) {
  cat("\n\n### ", list_run_name[[i]], "\n")
  print(list_output[[i]])
}
```



# Transcripts of All (per FOV)
```{r}
list_n_percent_type <- list_combined_data %>% 
  map(~ get_tx_n_percent_by_group_Fov(.x, group.by = "target_type"))
list_mean_sd_type <- list_combined_data %>% 
  map(~ get_tx_mean_sd_by_group_Target(.x, group.by = "target_type"))
```

## Count of transcripts  {.tabset .tabset-pills}
```{r, results='asis'}
list_output <- list_n_percent_type %>% 
  map(~ plt_n_by_group_Fov(.x))
y_max <- list_n_percent_type %>% map(~ .x$N) %>% unlist() %>% max()
y_range <- c(0, y_max)
list_output <- list_output %>% 
  map(
    ~ .x +
      scale_y_continuous(limits = y_range) +
      scale_x_discrete(labels = ~ .x %>% str_pad(width = nchar_fov, pad = "0"))
  )
  
cat("\n\n### ", "Combined\n")
print(plt_combined_grid(list_output))
for(i in seq_along(list_output)) {
  cat("\n\n### ", list_run_name[[i]], "\n")
  print(list_output[[i]])
}
```

## Percentage of Transcripts  {.tabset .tabset-pills}
```{r, results='asis'}
list_output <- list_n_percent_type %>% 
  map(~ plt_percent_by_group_Fov(.x))
y_range <- c(0, 100)
list_output <- list_output %>% 
  map(
    ~ .x +
      scale_y_continuous(limits = y_range) +
      scale_x_discrete(labels = ~ .x %>% str_pad(width = nchar_fov, pad = "0"))
  )
 
cat("\n\n### ", "Combined\n")
print(plt_combined_grid(list_output)) 
for(i in seq_along(list_output)) {
  cat("\n\n### ", list_run_name[[i]], "\n")
  print(list_output[[i]])
}
```


# Transcripts of Real Genes (per FOV)

## Count of transcripts  {.tabset .tabset-pills}
```{r, results='asis'}
list_output <- list_n_percent_type %>% 
  map(~ .x %>% filter(group.by == "Gene") %>% plt_n_by_group_Fov())
y_range <- get_pdata_range(list_output, "n", 1, 0)
list_output <- list_output %>% 
  map(
    ~ .x +
      scale_y_continuous(limits = y_range) +
      scale_x_discrete(labels = ~ .x %>% str_pad(width = nchar_fov, pad = "0"))
  )
  
cat("\n\n### ", "Combined\n")
print(plt_combined_grid(list_output))
for(i in seq_along(list_output)) {
  cat("\n\n### ", list_run_name[[i]], "\n")
  print(list_output[[i]])
}
```

## Percentage of Transcripts  {.tabset .tabset-pills}
```{r, results='asis'}
list_output <- list_n_percent_type %>% 
  map(~ .x %>% filter(group.by == "Gene") %>% plt_percent_by_group_Fov())
y_range <- get_pdata_range(list_output, "percent", 1, 0)
list_output <- list_output %>% 
  map(
    ~ .x +
      scale_y_continuous(limits = y_range) +
      scale_x_discrete(labels = ~ .x %>% str_pad(width = nchar_fov, pad = "0"))
  )
  
cat("\n\n### ", "Combined\n")
print(plt_combined_grid(list_output))
for(i in seq_along(list_output)) {
  cat("\n\n### ", list_run_name[[i]], "\n")
  print(list_output[[i]])
}
```

## Mean and Standard Deviation of Transcripts  {.tabset .tabset-pills}
```{r, results='asis'}
list_output <- list_mean_sd_type %>% 
  map(~ .x %>% filter(group.by == "Gene") %>% plt_mean_sd_by_group_Target())
y_range <- get_pdata_range(list_output, "mean_sd", 1, 0)
list_output <- list_output %>% 
  map(
    ~ .x +
      scale_y_continuous(limits = y_range) +
      scale_x_discrete(labels = ~ .x %>% str_pad(width = nchar_fov, pad = "0"))
  )
  
cat("\n\n### ", "Combined\n")
print(plt_combined_grid(list_output))
for(i in seq_along(list_output)) {
  cat("\n\n### ", list_run_name[[i]], "\n")
  print(list_output[[i]])
}
```

## Coefficient of Variation of Transcripts  {.tabset .tabset-pills}
```{r, results='asis'}
list_output <- list_mean_sd_type %>% 
  map(~ .x %>% filter(group.by == "Gene") %>% plt_cv_by_group_Target())
y_range <- get_pdata_range(list_output, "cv", 1, 0)
list_output <- list_output %>% 
  map(
    ~ .x +
      scale_y_continuous(limits = y_range) +
      scale_x_discrete(labels = ~ .x %>% str_pad(width = nchar_fov, pad = "0"))
  )
  
cat("\n\n### ", "Combined\n")
print(plt_combined_grid(list_output))
for(i in seq_along(list_output)) {
  cat("\n\n### ", list_run_name[[i]], "\n")
  print(list_output[[i]])
}
```


# Transcripts of Negative Probes (per FOV)

## Count of Transcripts  {.tabset .tabset-pills}
```{r, results='asis'}
list_output <- list_n_percent_type %>% 
  map(~ .x %>% filter(group.by == "Negative") %>% plt_n_by_group_Fov())
y_range <- get_pdata_range(list_output, "n", 1, 0)
list_output <- list_output %>% 
  map(
    ~ .x +
      scale_y_continuous(limits = y_range) +
      scale_x_discrete(labels = ~ .x %>% str_pad(width = nchar_fov, pad = "0"))
  )
  
cat("\n\n### ", "Combined\n")
print(plt_combined_grid(list_output))
for(i in seq_along(list_output)) {
  cat("\n\n### ", list_run_name[[i]], "\n")
  print(list_output[[i]])
}
```

## Percentage of Transcripts  {.tabset .tabset-pills}
```{r, results='asis'}
list_output <- list_n_percent_type %>% 
  map(~ .x %>% filter(group.by == "Negative") %>% plt_percent_by_group_Fov())
y_range <- get_pdata_range(list_output, "percent", 1, 0)
list_output <- list_output %>% 
  map(
    ~ .x +
      scale_y_continuous(limits = y_range) +
      scale_x_discrete(labels = ~ .x %>% str_pad(width = nchar_fov, pad = "0"))
  )
  
cat("\n\n### ", "Combined\n")
print(plt_combined_grid(list_output))
for(i in seq_along(list_output)) {
  cat("\n\n### ", list_run_name[[i]], "\n")
  print(list_output[[i]])
}
```


## Mean and Standard Deviation of Transcripts  {.tabset .tabset-pills}
```{r, results='asis'}
list_output <- list_mean_sd_type %>% 
  map(~ .x %>% filter(group.by == "Negative") %>% plt_mean_sd_by_group_Target())
y_range <- get_pdata_range(list_output, "mean_sd", 1, 0)
list_output <- list_output %>% 
  map(
    ~ .x +
      scale_y_continuous(limits = y_range) +
      scale_x_discrete(labels = ~ .x %>% str_pad(width = nchar_fov, pad = "0"))
  )
  
cat("\n\n### ", "Combined\n")
print(plt_combined_grid(list_output))
for(i in seq_along(list_output)) {
  cat("\n\n### ", list_run_name[[i]], "\n")
  print(list_output[[i]])
}
```

## Coefficient of Variation of Transcripts  {.tabset .tabset-pills}
```{r, results='asis'}
list_output <- list_mean_sd_type %>% 
  map(~ .x %>% filter(group.by == "Negative") %>% plt_cv_by_group_Target())
y_range <- get_pdata_range(list_output, "cv", 1, 0)
list_output <- list_output %>% 
  map(
    ~ .x +
      scale_y_continuous(limits = y_range) +
      scale_x_discrete(labels = ~ .x %>% str_pad(width = nchar_fov, pad = "0"))
  )
  
cat("\n\n### ", "Combined\n")
print(plt_combined_grid(list_output))
for(i in seq_along(list_output)) {
  cat("\n\n### ", list_run_name[[i]], "\n")
  print(list_output[[i]])
}
```


# Transcripts of False Codes (per FOV)

## Count of Transcripts  {.tabset .tabset-pills}
```{r, results='asis'}
list_output <- list_n_percent_type %>% 
  map(~ .x %>% filter(group.by == "SystemControl") %>% plt_n_by_group_Fov())
y_range <- get_pdata_range(list_output, "n", 1, 0)
list_output <- list_output %>% 
  map(
    ~ .x +
      scale_y_continuous(limits = y_range) +
      scale_x_discrete(labels = ~ .x %>% str_pad(width = nchar_fov, pad = "0"))
  )
  
cat("\n\n### ", "Combined\n")
print(plt_combined_grid(list_output))
for(i in seq_along(list_output)) {
  cat("\n\n### ", list_run_name[[i]], "\n")
  print(list_output[[i]])
}
```

## Percentage of Transcripts  {.tabset .tabset-pills}
```{r, results='asis'}
list_output <- list_n_percent_type %>% 
  map(~ .x %>% filter(group.by == "SystemControl") %>% plt_percent_by_group_Fov())
y_range <- get_pdata_range(list_output, "percent", 1, 0)
list_output <- list_output %>% 
  map(
    ~ .x +
      scale_y_continuous(limits = y_range) +
      scale_x_discrete(labels = ~ .x %>% str_pad(width = nchar_fov, pad = "0"))
  )
  
cat("\n\n### ", "Combined\n")
print(plt_combined_grid(list_output))
for(i in seq_along(list_output)) {
  cat("\n\n### ", list_run_name[[i]], "\n")
  print(list_output[[i]])
}
```


## Mean and Standard Deviation of Transcripts  {.tabset .tabset-pills}
```{r, results='asis'}
list_output <- list_mean_sd_type %>% 
  map(~ .x %>% filter(group.by == "SystemControl") %>% plt_mean_sd_by_group_Target())
y_range <- get_pdata_range(list_output, "mean_sd", 1, 0)
list_output <- list_output %>% 
  map(
    ~ .x +
      scale_y_continuous(limits = y_range) +
      scale_x_discrete(labels = ~ .x %>% str_pad(width = nchar_fov, pad = "0"))
  )
  
cat("\n\n### ", "Combined\n")
print(plt_combined_grid(list_output))
for(i in seq_along(list_output)) {
  cat("\n\n### ", list_run_name[[i]], "\n")
  print(list_output[[i]])
}
```

## Coefficient of Variation of Transcripts  {.tabset .tabset-pills}
```{r, results='asis'}
list_output <- list_mean_sd_type %>% 
  map(~ .x %>% filter(group.by == "SystemControl") %>% plt_cv_by_group_Target())
y_range <- get_pdata_range(list_output, "cv", 1, 0)
list_output <- list_output %>% 
  map(
    ~ .x +
      scale_y_continuous(limits = y_range) +
      scale_x_discrete(labels = ~ .x %>% str_pad(width = nchar_fov, pad = "0"))
  )
  
cat("\n\n### ", "Combined\n")
print(plt_combined_grid(list_output))
for(i in seq_along(list_output)) {
  cat("\n\n### ", list_run_name[[i]], "\n")
  print(list_output[[i]])
}
```


# Overall Error Rates (per FOV)
```{r}
list_error_rate <- list_mean_sd_type %>% 
  map(
    ~ .x %>% 
      pivot_wider(id_cols = fov, names_from = group.by, values_from = mean) %>% 
      mutate(
        across(c(Negative, SystemControl, Gene), ~ ifelse(is.na(.x), 0, .x)), 
        experimental_error = Negative / Gene * 100, 
        matching_error = SystemControl / Gene * 100
      )
  )
```

## Experimental Error (Mean Negative / Mean Real)  {.tabset .tabset-pills}
```{r, results='asis'}
list_output <- list_error_rate %>% 
  map(~ .x %>% rename(n = experimental_error) %>% plt_n_by_group_Fov())
y_range <- get_pdata_range(list_output, "n", 1, 0)
list_output <- list_output %>% 
  map(
    ~ .x +
      scale_y_continuous(limits = y_range) +
      scale_x_discrete(labels = ~ .x %>% str_pad(width = nchar_fov, pad = "0")) +
      labs(y = "Experimental Error (%)")
  )

cat("\n\n### ", "Combined\n")
print(plt_combined_grid(list_output))
for(i in seq_along(list_output)) {
  cat("\n\n### ", list_run_name[[i]], "\n")
  print(list_output[[i]])
}
```

## Matching Error (Mean False / Mean Real)  {.tabset .tabset-pills}
```{r, results='asis'}
list_output <- list_error_rate %>% 
  map(~ .x %>% rename(n = matching_error) %>% plt_n_by_group_Fov())
y_range <- get_pdata_range(list_output, "n", 1, 0)
list_output <- list_output %>% 
  map(
    ~ .x +
      scale_y_continuous(limits = y_range) +
      scale_x_discrete(labels = ~ .x %>% str_pad(width = nchar_fov, pad = "0")) +
      labs(y = "Matching Error (%)")
  )

cat("\n\n### ", "Combined\n")
print(plt_combined_grid(list_output))
for(i in seq_along(list_output)) {
  cat("\n\n### ", list_run_name[[i]], "\n")
  print(list_output[[i]])
}
```

